---
title: "Hepatic Fibrosis Degree Prediction"
subtitle: "Generated with Hepatic Fibrosis Degree Prediction App"
author: "By Andrea Vaca Tello"
date: '`r format(Sys.Date(),"%e de %B, %Y")`'
output:
  pdf_document:
    latex_engine: xelatex
    fig_caption: true
    
header-includes:
    - \usepackage{fancyhdr}
    
params:
  prediction: NA
  data_raw: !r NA
  data_pred: !r NA

---
<!-- QR image -->
\addtolength{\headheight}{1.0cm}
\pagestyle{fancyplain}
\rhead{\includegraphics[height=1.2cm]{Web_QR.png}}
\renewcommand{\headrulewidth}{0pt}


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment = NULL,
                      warning = FALSE, message = FALSE, 
                      fig.align="center")
```

```{r packages, include=FALSE}
# Load packages
library(knitr)
library(kableExtra)
library(ggplot2)
library(ggpubr)
library(dplyr)
library(rlang)
```

```{r script_plots, include=FALSE}
# Load script with plots functions
source("graficos_web_report.R")
```


# Results:

The posible results of the prediction are *F1* (Portal fibrosis without septa), *F2* (Portal fibrosis with some septa), *F3* (Numerous septa without cirrhosis) and *F4* (Cirrhosis).

The result* of the prediction with a 99% of precision is:  `r params$prediction`

\* Please note that these results are not a final diagnosis, but a support tool for specialists. The results have been generated with the \textcolor{blue}{\href{}{Hepatic Fibrosis Grade Prediction web application}}


# Data:

The data provided to make the prediction are:

```{r echo=FALSE}
# Data table
params$data_raw %>%
kable(booktabs = TRUE,format = "latex",digits = 1,
longtable=TRUE) %>%
kable_styling(
latex_options = c("striped", "condensed","repeat_header"),
position = "center",
full_width = FALSE,
repeat_header_text = "Continuation",
repeat_header_continued="Continue on the next page")


```


\newpage

# Plots:

The following graphs show the data used to train the predictive model and overlap the data and results used in the prediction, allowing a better understanding of the results:


```{r pie_plots, echo=FALSE, fig.height=4, fig.width=8}
# Pie plots
p1 <- plot_gender(dataset = params$data_pred) # Gender
p2 <- plot_degree(dataset = params$data_pred)  # Degree
final_plot <- ggarrange(p1, p2, legend = "top")
final_plot
```





```{r hist_box_plots, echo=FALSE, fig.height=3.5, fig.width=8}
# Distplots and Boxplots

## Age
p1 <- plot_distplot(dataset = params$data_pred, var = Age, var_name = "Age") 
p2 <- plot_boxplot( dataset = params$data_pred, var = Age, var_name = "Age")
final_plot <- ggarrange(p1, p2, legend = "top")
final_plot

## WBC
p1 <- plot_distplot(dataset = params$data_pred, var = WBC, var_name = "WBC")
p2 <- plot_boxplot( dataset = params$data_pred, var = WBC, var_name = "WBC")
final_plot <- ggarrange(p1, p2, legend = "top")
final_plot

## RBC
p1 <- plot_distplot(dataset = params$data_pred, var = RBC, var_name = "RBC")
p2 <- plot_boxplot( dataset = params$data_pred, var = RBC, var_name = "RBC")
final_plot <- ggarrange(p1, p2, legend = "top")
final_plot

## Plat
p1 <- plot_distplot(dataset = params$data_pred, var = Plat, var_name = "Plat")
p2 <- plot_boxplot( dataset = params$data_pred, var = Plat, var_name = "Plat")
final_plot <- ggarrange(p1, p2, legend = "top")
final_plot

## AST.1
p1 <- plot_distplot(dataset = params$data_pred, var = AST.1, var_name = "AST.1")
p2 <- plot_boxplot( dataset = params$data_pred, var = AST.1, var_name = "AST.1")
final_plot <- ggarrange(p1, p2, legend = "top")
final_plot

## ALT.1
p1 <- plot_distplot(dataset = params$data_pred, var = ALT.1, var_name = "ALT.1")
p2 <- plot_boxplot( dataset = params$data_pred, var = ALT.1, var_name = "ALT.1")
final_plot <- ggarrange(p1, p2, legend = "top")
final_plot

## RNA.Base
p1 <- plot_distplot(dataset = params$data_pred, var = RNA.Base, var_name = "RNA.Base")
p2 <- plot_boxplot( dataset = params$data_pred, var = RNA.Base, var_name = "RNA.Base")
final_plot <- ggarrange(p1, p2, legend = "top")
final_plot

```
























